\chapter{Subsmooth Case}

This chapter presents convergence results for ball-compact subsmooth moving sets.

\section{Subsmooth Sets}

\begin{definition}[Subsmooth set]
\label{def:subsmooth}
\uses{def:clarke_normal_cone}
\lean{MoreauSweeping.Subsmooth}
Let $S \subset H$ be a closed set. We say that $S$ is subsmooth at $x_0 \in S$ if for every $\varepsilon > 0$ there exists $\delta > 0$ such that
$$\langle \xi_2 - \xi_1, x_2 - x_1 \rangle \ge -\varepsilon \|x_2 - x_1\|$$
whenever $x_1, x_2 \in B[x_0, \delta] \cap S$ and $\xi_i \in N(S; x_i) \cap \mathbb{B}$ for $i \in \{1,2\}$.
\end{definition}

\begin{definition}[Equi-uniformly subsmooth family]
\label{def:equi_uniformly_subsmooth}
\uses{def:subsmooth}
\lean{MoreauSweeping.EquiUniformlySubsmooth}
A family $(S(t))_{t\in I}$ of closed sets is called equi-uniformly subsmooth if for all $\varepsilon > 0$, there exists $\delta > 0$ such that for all $t \in I$, the subsmoothness inequality holds uniformly.
\end{definition}

\begin{remark}
The class of subsmooth sets includes both convex and uniformly prox-regular sets, making it a very general framework for the sweeping process.
\end{remark}

\section{Ball Compactness}

\begin{definition}[Ball-compact sets]
\label{def:ball_compact}
A set $S \subset H$ is ball-compact if $S \cap r\mathbb{B}$ is compact for all $r > 0$.
\end{definition}

\begin{remark}
Ball-compactness is weaker than compactness but sufficient for many existence results in infinite-dimensional Hilbert spaces.
\end{remark}

\section{Stability Result}

\begin{lemma}[Stability for subsmooth sets]
\label{lem:stability_subsmooth}
\uses{def:distance,def:equi_uniformly_subsmooth}
\lean{MoreauSweeping.stability_subsmooth}
\uses{def:subsmooth, def:equi_uniformly_subsmooth, lem:proximal_normal_characterization}
Let $\mathcal{C} = \{C_n\}_{n\in\mathbb{N}} \cup \{C\}$ be a family of nonempty, closed, and equi-uniformly subsmooth sets. Under appropriate convergence assumptions, certain stability properties hold for the subdifferentials of distance functions.
\end{lemma}

\section{Convergence Result}

\begin{theorem}[Convergence for subsmooth sets]
\label{thm:convergence_subsmooth}
\uses{thm:algorithm_properties,eq:sweeping_process,def:hausdorff,def:ball_compact,lem:stability_subsmooth}
\lean{MoreauSweeping.convergence_subsmooth}
\uses{thm:algorithm_properties, lem:stability_subsmooth, def:ball_compact}
For ball-compact subsmooth moving sets, the catching-up algorithm with approximate projections converges to a solution of the sweeping process.
\end{theorem}
